### 2011-02-09 paper/results.tex

% Present the quantitative results of your experiments. Graphical data
% presentation such as graphs and histograms are frequently better 
% than tables. Explain what are the basic differences revealed in the 
% data. If your method is stochastic or you analyze multiple datasets, 
% calculate mean and standard error for every quantitative
% performance result you show based on multiple runs.

\edit{proofread this.}

\subsection{Exploration of Parameter Space}

In addition to running strategies to optimize parameterized gaits, we
also wanted to investigate the space of possible gaits.  To accomplish
this, we selected a parameter vector that resulted in motion, but not
an exceptional gait, and plotted performance along each dimension
individually.  In addition, we duplicated each measurement to be able
to estimate the measurement noise at each point.  Results for this
exploration are shown in \figref{explore_dim_1} through
\figref{explore_dim_5}.  As is shown in the figures, some dimensions
are smoother than others, and some measurements are fairly noisy.

>>>>

% Outline:
% - exploration of parameter space
% - parameterized optimization results, discussion
% - HyperNEAT results, discussion

\subsection{Exploration of Parameterized Gait Space}

%\edit{Jeff: proofread}

Before attempting to use the learning methods
(\secref{learningMethods}) to optimize the chosen family of
parameterized gaits (SineModel5, \secref{motionModel}), we did a brief
experiment to explore the five dimensions of the parameter space. To
accomplish this, we first selected a random parameter vector that resulted
in motion, but not an exceptional gait.

Then, in five different experiments, we varied each parameter
individually and plotted performance versus each changing parameter.
In addition, we duplicated each measurement to be able to estimate
standard deviation of the measurement noise at each point.  Results
for this exploration are shown in \figref{explore_dim_1} through
\figref{explore_dim_5}.  As is shown in the figures, some dimensions
are smoother than others, and some measurements are fairly noisy.
